---
title: "individual expect"
author: "Xiaomeng"
date: "7/13/2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# initiate libraries\
```{r, include = FALSE}
library(tidyverse)
library(plyr)
library(dplyr)
```

# importe origin data
```{r, include = FALSE}
low <- read_csv("/Work/Research/PHD/Dissertation 2017/AXBX_2016/subjective_rating/subj_rating_LA.csv", na = ".")

```

# arrange by symbolvec 
```{r}
low_2 <- low %>% 
         arrange(phase, symbolvec)
```



# create a column for repetition numbers
```{r,  include = FALSE}
## trial numbers in each phases
rep1=30
rep2=32
rep3=65
rep4=30

##
### rep1_1 = 7 + 1
### rep1_2 = 7 + 1
### rep1_3 = 7
### rep1_4 = 7
r11 = (1:8)
r12 = (1:8)
r13 = (1:7)
r14 = (1:7)
r1 = c(r11, r12, r13, r14)
r1

###rep2_1 = 8
###rep2_2 = 8
###rep2_3 = 8
###rep2_4 = 8
r21 = (1:8)
r22 = (1:8)
r23 = (1:8)
r24 = (1:8)
r2 = c(r21, r22, r23, r24)
r2

###rep3_1 = 17
###rep3_2 = 16
###rep3_3 = 16
###rep3_4 = 16
r31 = (1:17)
r32 = (1:16)
r33 = (1:16)
r34 = (1:16)
r3 = c(r31, r32, r33, r34)
r3


###rep4_1 = 7 + 1
###rep4_2 = 7 + 1
###rep4_3 = 7
###rep4_4 = 7
r41 = (1:8)
r42 = (1:8)
r43 = (1:7)
r44 = (1:7)
r4 = c(r41, r42, r43, r44)
r4

rep = c(r1, r2, r3, r4)
View(rep)

# add rep as a new column to low_1
low_3 <- mutate(low_2, rep_num = rep)
View(low_3)


```

#Gather sbj into one column
```{r}
low_4 <- 
 low_3 %>% 
 gather("s10", "s11", "s12", "s13", "s15","s17", "s18", "s19", "s2", "s21",
       "s24", "s25", "s26", "s27", "s29",
       "s3", "s34", "s39", "s44", "s5", "s6", "s9", key = "sbj", value = "expect")


```

#sum_4 <- ddply(low_4, c("phase", "symbolvec", "sbj"), summarise,
               N    = length(expect),
               mean = mean(expect),
               sd   = sd(expect),
               se   = sd / sqrt(N))
               
               
#specify which sbj
```{r}

sbj = 10

low_sbj <- low_4 %>% 
  filter(sbj == "s10") %>% 
   select(phase, symbolvec,rep_num, expect)



```

# decide ABXC
```{r}


# 1 = down, 2 = up, 3 = right, 4 = left

# A=down B=up X=right C=left
# A = 1, B = 2, X = 3, C = 4
set1 = c(5, 9, 13, 18, 26, 29, 37, 41, 45, 48, 52)
  
set2= c(2, 6, 11, 15, 19, 27, 34, 38, 42, 46, 49, 54)

setI=c(set1, set2)

# A=up B=down X=left C=right
# A = 2, B = 1, X = 4, C = 3
  
set3= c(3, 7, 10, 16, 20, 24, 28, 31, 35, 39, 43)
  
set4=c(4, 12, 17, 21, 25, 36, 40, 44, 47, 50)

setII=c(set3, set4)

if (sbj %in% setI)
 {old = ("1234")
 new = ("ABXC")
 symbol = chartr(old, new, low_sbj$symbolvec)
 data <- low_sbj %>% mutate(symbol=symbol)
 df <- select(data, phase, symbol, rep_num, expect)
 }

if (parse_number(sbj) %in% setII)
 {old = ("1234")
 new = ("BACX")
 symbol = chartr(old, new, low_sbj$symbolvec)
 data <- low_sbj %>% mutate(symbol=symbol)
 df <- select(data, phase, symbol, rep_num, expect)
}
```


# data visualization
```{r}
# calculate stand deviations
df_sum <- ddply(df, c("phase", "symbol"), summarise,
               N    = length(expect),
               mean = mean(expect),
               sd   = sd(expect),
               se   = sd / sqrt(N))


# draw bar plot w/ error bars
pd <- position_dodge(0.9)
plot_s10 <- df_sum %>% 
  mutate(symbol = factor(symbol, levels = c("A", "B", "X", "C"))) %>% 
  ggplot(aes(fill = symbol, x=phase, y=mean)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_errorbar(aes(x=phase, ymin=mean-sd, ymax=mean+sd, group=factor(symbol)), width=0.4, colour="orange", alpha=0.9, size=1, position = pd)
plot_s10  
```

